% Standalone LaTeX file (Overleaf-ready)
% Guide 09: Scoring Runbook (Localized Fine Features and Repair)
% Compile with: PDFLaTeX

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{enumitem}
\usepackage{siunitx}
\usepackage{fancyhdr}

\definecolor{darkblue}{rgb}{0.0, 0.0, 0.5}
\hypersetup{
  colorlinks=true,
  linkcolor=darkblue,
  urlcolor=darkblue,
  citecolor=darkblue,
  pdftitle={Guide 09: Scoring Runbook},
  pdfauthor={Open Research Draft}
}

\sisetup{detect-all=true}

\newcommand{\ProgramName}{Layer--Score--Layer Neuromorphic Tile Program}
\newcommand{\GuideID}{Guide 09}
\newcommand{\GuideTitle}{Scoring Runbook (Localized Fine Features and Repair)}
\newcommand{\DocVersion}{v1.1 (standalone)}
\newcommand{\DocDate}{\today}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}

\pagestyle{fancy}
\fancyhf{}
\lhead{\GuideID: \GuideTitle}
\rhead{\DocVersion}
\cfoot{\thepage}

\begin{document}

\begin{titlepage}
  \centering
  \vspace*{1.0in}
  {\LARGE \GuideID: \GuideTitle\par}
  \vspace{0.25in}
  {\Large \ProgramName\par}
  \vspace{0.35in}
  {\large \DocVersion\par}
  \vspace{0.10in}
  {\large \DocDate\par}
  \vfill
  \begin{minipage}{0.93\textwidth}
  \small
  \textbf{Purpose.} Define and enforce the rules for high-resolution ``scoring'' (localized fine-feature definition and repair) so it remains a scalpel rather than a throughput trap. This guide makes scoring usage a tracked KPI with explicit budgets and escalation triggers.
  \\
  \\
  \textbf{Safety note.} This guide assumes scoring tools (e.g., EBL/FIB or equivalents) are operated in professional/shared facilities or by trained staff on commercial systems.
  \end{minipage}
  \vspace*{0.6in}
\end{titlepage}

\tableofcontents
\newpage

\section{Purpose and Operating Principle}
\textbf{Scoring must not be on the per-device critical path.} If scoring scales with array size, the program must redesign the process or accept a smaller scale target.

\section{Core Deliverables}
\begin{enumerate}[leftmargin=*,itemsep=2pt]
\item Allowed vs forbidden scoring use-cases policy
\item ROI budgets (maximum scored area per die and per run)
\item Verification protocol (pre-score and post-score evidence)
\item Score justification record (why it was needed; measurable benefit)
\item \textbf{Scoring budget KPI and escalation triggers} (mandatory)
\end{enumerate}

\section{Policy: Allowed vs Forbidden Use-Cases}
\subsection{Allowed}
\begin{itemize}[leftmargin=*,itemsep=2pt]
\item Critical region definition in small ROIs when baseline lithography cannot meet requirements.
\item Trim/repair of opens/shorts for research prototypes.
\item Stitch fixes at known overlay-limited interfaces.
\item Creation of master molds (optional), when replication is used later.
\end{itemize}

\subsection{Forbidden}
\begin{itemize}[leftmargin=*,itemsep=2pt]
\item Full-area patterning or routine routing layers.
\item Any use that scales linearly with array size without a formal exception.
\item ``Convenience scoring'' without documented justification and evidence.
\end{itemize}

\section{Scoring Budget KPI (Mandatory)}
\textbf{You must track these metrics for every run that uses scoring:}
\begin{itemize}[leftmargin=*,itemsep=2pt]
\item Total scored area per die (units: square micrometer, or square millimeter as appropriate).
\item Total scored area per run.
\item Number of scored ROIs per die.
\item Scoring time per run (if measurable).
\end{itemize}

\section{Gate: Scoring Must Not Become Per-Device}
\textbf{Gate rule:} If scoring is required for \emph{every device} (or scales linearly with array size), the process is considered \textbf{non-scalable} at the current node.

\textbf{Required response (choose at least one):}
\begin{itemize}[leftmargin=*,itemsep=2pt]
\item Redesign for baseline lithography capability.
\item Reduce the target array size.
\item Change topology to remove the fine-feature dependency.
\item Document a formal exception and accept the throughput limitation.
\end{itemize}

\section{Escalation Triggers}
\textbf{If either occurs in two consecutive runs:}
\begin{itemize}[leftmargin=*,itemsep=2pt]
\item scored area exceeds the ROI budget, or
\item scoring becomes a per-device necessity,
\end{itemize}
\textbf{then a redesign review is mandatory} before the next run is scheduled.

\section{Step-by-Step Procedure (Operational)}
\begin{enumerate}[leftmargin=*,itemsep=2pt]
\item Define scoring intent and ROI budgets in the traveler before scoring begins.
\item Capture pre-score images at standard magnification and sites.
\item Perform scoring only within approved ROIs.
\item Capture post-score images (same sites and magnification).
\item Perform an electrical sanity check if applicable.
\item File a score justification record including measurable benefit and evidence.
\end{enumerate}

\section{Exit Criteria}
Guide 09 is complete (operationally) when:
\begin{enumerate}[leftmargin=*,itemsep=2pt]
\item scoring usage is bounded by explicit ROI budgets,
\item scoring KPIs are logged in every run summary that uses scoring,
\item scoring is not required per-device to achieve the target scale,
\item any exceptions are documented and accepted as throughput tradeoffs.
\end{enumerate}

\end{document}
